Comparison of C Abundance Observations

### 2025-11-14 carbon_paper/tex/survey_comparison.tex
near-submission draft

% MAIN DOCUMENT
\title{Comparison of C inn observations}

@@

\subsection{Large Spectroscopic Surveys}
In general (see Fig.~\ref{fig:other_surveys}, all surveys (except for GALAH, see below) agree in both the \caah\ and \caafe\ trends, up to a \about{0.2} dex offset. Changing our adopted equilibrium trend to any of these would only affect the yield scale, which is already a known degeneracy in chemical evolution modeling.

We do not renormalize surveys and instead use reported abundances. Each survey sets zero points in slightly different manners, and given the systematic uncertainty in this step, the absolute abundance scale of a survey is less precise than abundance trends.

% \begin{figure}
%     \centering
%     \includegraphics{c+n.pdf}
%     \caption{[C+N/Mg]. This figure is likely getting cut, check if looks good with full sample (reassuring), and maybe look at [Mg/Fe] here too, but if agrees, we do not need it anymore...}
%     \label{fig:cn}
% \end{figure}

@@

The {\bf Gaia-ESO} survey (Gilmore + 2022, Randich+2022) is a large ($10^5$) stellar spectroscopic instrument using FLAMES/VLT with both the GIRAFFE (R $\sim$ 20k) and UVES ($R\sim 50k$) spectrographs. 
Here, we use the catalogue published in  \citep{hourihane+2023} containing 114,816 stars.
GSO uses the Grevesse 2007 solar abundances for the low resolution survey but does not calibrate (?) the high resolution survey, so we apply XXX corrections.
WG10 uses 5380.33, 6587.61 as the C lines (worley+2024).
However, for high resolution observations (WG11), C is derived from the swan bands:
C2 Swan (1, 0) band head at 5135 Å and C2 Swan (0, 1) band head at 5635.5 Å
(Tautvaišiene˙ et al. 2015); discussed as but are not sensitive to non-local thermodynamic equilibrium (NLTE) deviations (cf. Clegg et al. 1981;
Gustafsson et al. 1999)

our flags are
\begin{itemize}
    \item No flags in SNR, SRP, BIN, SSA, IPA, PSC< EML
    \item errors in LOGG < 0.5
    \item errors in Teff < 200
    \item logg >= 3.5
    \item no NaN C, Mg, Fe, and respective errors.
\end{itemize}

@@

\begin{table}
\centering
\begin{tabular}{lrlll}
\hline
QSO & redshift & C/O & O/H & study \\
\hline
HS 0105+1619 & 2.535998 & $0.23 \pm 0.07$ & $-1.75 \pm 0.03$ & omera+01 \\
J1358+6522 & 3.067259 & $-0.27 \pm 0.06$ & $-2.34 \pm 0.06$ & cooke+14 \\
J0955+4116 & 3.279908 & $-0.46 \pm 0.15$ & $-2.47 \pm 0.06$ & welsh+2022 \\
J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & ellison+10 \\
J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
Q1243+307 & 2.525640 & $0.24 \pm 0.03$ & $-2.79 \pm 0.03$ & cooke+18 \\
PKS1937-101 & 3.572400 & $1.56 \pm 0.13$ & $-2.57 \pm 0.13$ & riemer-sorensen+17 \\
Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & dessauges-zavadsky+03 \\
Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & dessauges-zavadsky+03 \\
J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & dessauges-zavadsky+03 \\
J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.69 \pm 0.17$ & srianand+10 \\
Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & pettini+08 \\
J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & pettini+08 \\
J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & pettini+08 \\
Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & pettini+08 \\
J1332+0052 & 3.421086 & $-0.03 \pm 0.02$ & $-1.72 \pm 0.02$ & kislitsyn+24 \\
J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
\hline
\end{tabular}
\end{table}
C abundances are measured in XXXX.

@@

\begin{longtable}{lllll}

@@

SDSS J094401.87-003832.1 & centre & $-1.15 \pm 0.06$ & $-1.00 \pm 0.07$ & senchyna+17 \\
SDSS J102429.25+052450.9 & centre & $-0.60 \pm 0.20$ & $-0.89 \pm 0.04$ & senchyna+17 \\
UGC 5189 & SDSS J094256.74+092816.2, & $-0.53 \pm 0.45$ & $-0.57 \pm 0.06$ & senchyna+17 \\

@@

Mrk 960 & NaN & $-0.41 \pm 0.39$ & $-0.70 \pm 0.19$ & pena-guerreno+17 \\

@@

\begin{longtable}{lllll}
\hline
galaxy & region & C/O & O/H & study \\
\hline
NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
MW & Sh 2-311 & $-0.10 \pm 0.14$ & $-0.24 \pm 0.05$ & mendez-delgado+22 \\
MW & NGC 2579 & $-0.14 \pm 0.09$ & $-0.26 \pm 0.03$ & mendez-delgado+22 \\
MW & NGC 3576 & $-0.02 \pm 0.08$ & $-0.08 \pm 0.04$ & mendez-delgado+22 \\
MW & NGC 3603 & $0.04 \pm 0.12$ & $-0.10 \pm 0.05$ & mendez-delgado+22 \\
MW & M8 & $0.04 \pm 0.10$ & $-0.11 \pm 0.04$ & mendez-delgado+22 \\
MW & M16 & $0.03 \pm 0.15$ & $-0.01 \pm 0.05$ & mendez-delgado+22 \\
MW & M17 & $0.26 \pm 0.06$ & $-0.06 \pm 0.02$ & mendez-delgado+22 \\
MW & M20 & $0.02 \pm 0.25$ & $-0.10 \pm 0.06$ & mendez-delgado+22 \\
MW & M42 & $0.03 \pm 0.07$ & $-0.16 \pm 0.02$ & mendez-delgado+22 \\
M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
M101 & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
M101 & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
M101 & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
M101 & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
M101 & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
M101 & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
M101 & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
M101 & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
M101 & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
NGC 300 & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
NGC 300 & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
M33 & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
M33 & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
LMC & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
LMC & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
LMC & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
SMC & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
SMC & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
NGC 6822 & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
NGC 5408 & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
M31 & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
M33 & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
M33 & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
NGC 2366 & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
NGC 2403 & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
NGC 2403 & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
\hline
\end{longtable}

>>>>

% MAIN DOCUMENT
\title{Comparison of C Abundance Observations}

@@

\subsection{Large Spectroscopic Surveys}
In general (see Fig.~\ref{fig:other_surveys}, all medium-high large spectroscopic surveys agree in both the \caah\ and \caafe\ trends, up to a \about{0.2} dex offset. Changing our adopted equilibrium trend to any of these would only affect the yield scale, which is already a known degeneracy in chemical evolution modelling.

We do not re normalize surveys and instead use reported abundances. Each survey sets zero points in slightly different manners, and given the systematic uncertainty in this step, the absolute abundance scale of a survey is less precise than abundance trends.

@@

\subsubsection{{\it Gaia}-ESO}
The Gaia-ESO survey (Gilmore + 2022, Randich+2022) is a large ($10^5$) stellar spectroscopic instrument using FLAMES/VLT with both the GIRAFFE (R $\sim$ 20k) and UVES ($R\sim 50k$) spectrographs. 
Here, we use the catalogue published in  \citep{hourihane+2023} containing 114,816 stars.
GSO uses the Grevesse 2007 solar abundances for the low resolution survey but does not calibrate (?) the high resolution survey, so we apply XXX corrections.
WG10 uses 5380.33, 6587.61 as the C lines (worley+2024).
However, for high resolution observations (WG11), C is derived from the swan bands:
C2 Swan (1, 0) band head at 5135 Å and C2 Swan (0, 1) band head at 5635.5 Å
(Tautvaišiene˙ et al. 2015); discussed as but are not sensitive to non-local thermodynamic equilibrium (NLTE) deviations (cf. Clegg et al. 1981;
Gustafsson et al. 1999)

Our selection criteria are
\begin{itemize}
    \item No flags in SNR, SRP, BIN, SSA, IPA, PSC< EML
    \item errors in LOGG < 0.5
    \item errors in Teff < 200
    \item logg >= 3.5
    \item no NaN C, Mg, Fe, and respective errors.
\end{itemize}

@@

\begin{table}
\centering
\small
\begin{tabular}{lrlll}
\hline
QSO & redshift & C/O & O/H & study \\
\hline
HS 0105+1619 & 2.535998 & $0.23 \pm 0.07$ & $-1.75 \pm 0.03$ & omera+01 \\
J1358+6522 & 3.067259 & $-0.27 \pm 0.06$ & $-2.34 \pm 0.06$ & cooke+14 \\
J0955+4116 & 3.279908 & $-0.46 \pm 0.15$ & $-2.47 \pm 0.06$ & welsh+2022 \\
J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & ellison+10 \\
J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
Q1243+307 & 2.525640 & $0.24 \pm 0.03$ & $-2.79 \pm 0.03$ & cooke+18 \\
PKS1937-101 & 3.572400 & $1.56 \pm 0.13$ & $-2.57 \pm 0.13$ & riemer-sorensen+17 \\
Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & dessauges-zavadsky+03 \\
Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & dessauges-zavadsky+03 \\
J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & dessauges-zavadsky+03 \\
J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.69 \pm 0.17$ & srianand+10 \\
Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & pettini+08 \\
J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & pettini+08 \\
J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & pettini+08 \\
Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & pettini+08 \\
J1332+0052 & 3.421086 & $-0.03 \pm 0.02$ & $-1.72 \pm 0.02$ & kislitsyn+24 \\
J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
\hline
\end{tabular}
\end{table}

C abundances are measured in XXXX.

@@

\small
\begin{longtable}{p{2.5cm}p{2.5cm}lll}
    \caption{Caption} \\

@@

    SDSS J094401.87 -003832.1 & centre & $-1.15 \pm 0.06$ & $-1.00 \pm 0.07$ & senchyna+17 \\
    SDSS J102429.25 +052450.9 & centre & $-0.60 \pm 0.20$ & $-0.89 \pm 0.04$ & senchyna+17 \\
    UGC 5189 & SDSS J094256.74 +092816.2, & $-0.53 \pm 0.45$ & $-0.57 \pm 0.06$ & senchyna+17 \\

@@

    im & NaN & $-0.41 \pm 0.39$ & $-0.70 \pm 0.19$ & pena-guerreno+17 \\

@@

\relax

\begin{longtable}{llllll}
\caption{Recombination Line Abundances of C from a selection of source} \\

\toprule
galaxy & class & region & [C\_O] & [O\_H] & study \\
\midrule
NGC 6822 & dwarf & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
MW & MW & Sh 2-311 & $-0.10 \pm 0.13$ & $-0.24 \pm 0.04$ & mendez-delgado+22 \\
MW & MW & NGC 2579 & $-0.15 \pm 0.09$ & $-0.25 \pm 0.03$ & mendez-delgado+22 \\
MW & MW & NGC 3576 & $-0.03 \pm 0.10$ & $-0.07 \pm 0.06$ & mendez-delgado+22 \\
MW & MW & NGC 3603 & $0.03 \pm 0.12$ & $-0.09 \pm 0.05$ & mendez-delgado+22 \\
MW & MW & M8 & $0.03 \pm 0.10$ & $-0.10 \pm 0.04$ & mendez-delgado+22 \\
MW & MW & M16 & $0.03 \pm 0.16$ & $-0.01 \pm 0.06$ & mendez-delgado+22 \\
MW & MW & M17 & $0.25 \pm 0.08$ & $-0.05 \pm 0.04$ & mendez-delgado+22 \\
MW & MW & M20 & $0.02 \pm 0.26$ & $-0.10 \pm 0.07$ & mendez-delgado+22 \\
MW & MW & M42 & $0.03 \pm 0.08$ & $-0.16 \pm 0.03$ & mendez-delgado+22 \\
M101 & spiral & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
M101 & spiral & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
M101 & spiral & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
M101 & spiral & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
M101 & spiral & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
M101 & spiral & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
M101 & spiral & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
M101 & spiral & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
M101 & spiral & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
M101 & spiral & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
NGC 300 & spiral & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & spiral & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
NGC 300 & spiral & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & spiral & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
M33 & spiral & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
M33 & spiral & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
LMC & magellanic & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
LMC & magellanic & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
LMC & magellanic & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & magellanic & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & magellanic & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & magellanic & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
SMC & magellanic & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & magellanic & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
SMC & magellanic & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
NGC 6822 & dwarf & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
NGC 5408 & dwarf & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
M31 & spiral & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
M33 & spiral & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
M33 & spiral & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
NGC 2366 & magellanic & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
NGC 2403 & spiral & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
NGC 2403 & spiral & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
NGC 2403 & spiral & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
\bottomrule
\end{longtable}
